Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-12 ms_pre_post.Rmd
Some initial work on the first paragraph revision

<!--- Reproductive decisions expressed among interacting individuals directly affect individual fitnesses and the genotypes and viabilities of resulting offspring, and thereby profoundly affect evolutionary dynamics through the differential inheritence of alleles over generations [@Pizzari2012; @Wright2013; @Wild2014; @Liao2015; @Reid2016]. For example, how frequently a focal female mates is a reproductive decision that can directly and indirectly affect her fitness, and potentially alter the distribution of genotypes and patterns of inheritence within a population [e.g., @Cornell2007; @Diaz2010; @Okada2015; @Roberts2015a; @Worthington2016]. Her mating frequency and expression of mate choice might be affected by the genetic quality or complementarity of available potential mates, and her choosiness might additionally be expressed after mating has taken place through post-copulatory mechanisms [@Parker1983; @Parker2006; @Kuijper2012]. Female choice might therefore be realised by evolution of multiple, potentially interdependent, behavioural and physiological phenotypes operating in tandem. However, no general modelling framework predicts the conditions under which female mating frequency, pre-copulatory choice, and post-copulatory choice evolve together, meaning that there are no formal hypotheses for predicting the relevance of these reproductive decisions across different biological systems. --->

Polyandry, defined as female multiple mating within a single reproductive bout, is a reproductive strategy that simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms. One key choice for females is the decision to prefer, avoid, or tolerate breeding with relatives ['inbreeding'; @Szulkin2012]. Inbreeding often reduces the fitness of inbred offspring [@Charlesworth1999; @Keller2002; @Charlesworth2009], and polyandry has been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007]. In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate. In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen. However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring. If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].

@@

<!--- Rubbish: is unlikely to be simultaneous. Testing whether or not initially rare alleles underlying inbreeding avoidance can successfully invade a population Even if invasion fitness of alleles underlying inbreeding avoidance are high when mating and fertilisation is random with respect to relatedness, initial invasion of Initial evolution of pre- and post-copulatory inbreeding avoidance strategies is unlikely to be simultaneous, so to predict evolutionary outcomes, it is necessary to consider evolution when one inbreeding avoidance strategy is initially rare, and the other strategy is common. For example, if pre-adaptation or rapid selection resulted in the fixation of alleles underlying adaptive pre-copulatory inbreeding avoidance, then alleles underlying post-copulatory inbreeding avoidance might be precluded from invading a population in which post-copulatory choice is not already expressed because the effect that such invading alleles had on decreasing total inbreeding avoidance would be weak or negligible.  --->

<!--- It is therefore necessary to consider evolution of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy when each evolves in a population where its complementary inbreeding strategy is evolutionarily constrained or already fixed as an adaptation. --->

<!--- Overall, to predict evolution of polyandry and inbreeding strategies, it is therefore necessary to model costs associated with polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy. --->

<!--- Inbreeding, defined as breeding between relatives, directly affects inheritence of identical-by-descent alleles and the viability of inbred offspring, meaning that the decision to prefer, avoid, or tolerate (i.e., mate randomly with respect to relatedness) inbreeding is predicted to have profound effects on individual fitness [@Parker2006; @Kokko2006; @Szulkin2012; @Duthie2015a]. Viability of inbred offspring typically decreases with increasing relatedness between parents [termed 'inbreeding depression'; @Keller2002; @Charlesworth2009]. If inbreeding depression is sufficiently weak, selection for female inbreeding preference is predicted because inbreeding increases the reproductive success of a focal female's male relative, thereby increasing the number of identical-by-descent allele copies present in her offspring [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a]. However, if inbreeding depression is moderate to strong, selection for female inbreeding avoidance is predicted [Duthie and Reid *in press*; @Duthie]. Female inbreeding strategy can be enacted before or after copulation occurs [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015]. However, models of inbreeding do not consider pre-copulatory inbreeding strategy (hereafter 'pre-copulatory inbreeding strategy') and post-copulatory inbreeding strategy (hereafter 'post-copulatory inbreeding strategy') jointly, meaning that it is unclear when selection for either or both strategies is predicted in empirical systems.  --->

<!--- Critically, evolution of post-copulatory inbreeding strategy is precluded if females only mate with one male, meaning that evolution of polyandry (defined as female multiple mating within a single reproductive bout) is intrinsically tied to female post-copulatory inbreeding strategy. Although polyandry is commonplace in wild populations, the regularity with which it is observed in the wild remains theoretically puzzling because engaging in polyandry does not necessarily increase the number of offspring that a female produces, meaning that the fitness benefits associated with polyandry are not always clear [@Parker2013; @Taylor2014]. It has been hypothesised that females can acheive a net fitness benefit if polyandry provides them with additional opportunities to adjust their inbreeding through copulations with additional males [e.g., @Tregenza2002; @Akcay2007; @Lehtonen2015].  However, no models quantify the degree to which expression of biased paternity resulting from evolving post-copulatory inbreeding strategy can feedback to drive evolution of polyandry in populations of potentially inbreeding females and males with biologically realistic distributions of relatedness. --->

<!--- Evolution of post-copulatory inbreeding strategy might increase selection for polyandry, but evolutionary feedbacks between post-copulatory inbreeding strategy and polyandry might also be contingent upon evolution of pre-copulatory inbreeding strategy, thereby leading to complex evolutionary dynamics between inbreeding strategies and polyandry. For example, if females can acheive their desired degree of inbreeding through mate choice alone, then subsequent polyandry and post-copulatory inbreeding strategy might be superfluous for increasing female fitness. Alternatively, if females are often unsuccessful at realising their pre-copulatory inbreeding strategy due to factors such as sexual conflict over mating and resulting male coercion [e.g., @Parker2006], limited kin recognition amongst potential mates [e.g., @Penn2010], or simply the inherent stochasticity associated with mate encounters or expression of mate choice based on inbreeding [e.g., @Kokko2006; @Duthie], then selection on post-copulatory inbreeding strategy might occur to reinforce pre-copulatory inbreeding strategy. In empirical systems where inbreeding depression is severe and inbreeding avoidance is therefore beneficial, expression of pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy have been observed across diverse taxa [e.g., @Gasparini2011; @Tuni2013; @Firman2015; @Fischer2015; @Daniel2015]. However, no models predict *a priori* which of these inbreeding strategies should be observed when inbreeding depression is sufficiently severe to make inbreeding avoidance adaptive. --->

<!--- Evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy will ultimately be determined by the, potentially interacting, fitness benefits and costs of each phenotype. Given severe inbreeding depression, phenotypes will increase a focal female's fitness if they cause her to avoid breeding with close relatives [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a]. However,  --->

<!--- Selection for pre-copulatory inbreeding strategy versus post-copulatory inbreeding strategy and associated polyandry might also depend evolutionary constraints, or on existing phenotypes in the population. For example, if phenotypes biasing fertilisation to avoid inbreeding are precluded by evolutionary constraints [@Bradshaw1991; @Futuyma2010], then inbreeding avoidance might only be possible before copulation occurs, perhaps strengthening selection for pre-copulatory inbreeding strategy and weakening selection for polyandry. Alternatively, evolution of female pre-copulatory inbreeding strategy might be precluded due to severely limited kin recognition or the inability to resist male coercion given sexual conflict [@Arnqvist2005a; @Parker2006; @Penn2010]. In such conditions, females might only be able to express choice through post-copulatory inbreeding strategy, perhaps strengthening selection for inbreeding avoidance through polyandry and post-copulatory mechanisms. Selection for inbreeding mating or fertilisation strategy might also be weak or negligible if the strategy is redundant due to the presence of an already established adaptive inbreeding strategy (e.g., if females already successfully avoid inbreeding during mate encounters, then they might be unable to increase their fitness further by biasing fertilisation after mating has occurred). --->

<!--- Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate phenotypes including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy). --->

@@

<!--- that constraints on evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding strategy) will increase the strength of selection on evolution of a complementary inbreeding strategy (e.g., post-copulatory inbreeding strategy), and that --->

@@

<!--- In the case of tendency to engage in polyandry, the cost of $P_{p}$ ($c_{P}$) is interpreted biologically as a cost associated with mate searching or courtship [e.g., @Rowe1988; @Rowe1994; @Ronkainen1994; @Koga1998; @Lasley-Rasher2012]. For pre-copulatory inbreeding strategy, the cost of $M_{p}$ ($c_{M}$) is interpreted biologically as a cost associated with risk of mating failure due to females being overly choosy [e.g., @Kokko2013], and for post-copulatory inbreeding strategy, the cost of $F_{p}$ ($c_{F}$) is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilisation for inbreeding avoidance or inbreeding preference [e.g., @Gasparini2011]. --->

@@

<!--- We simulate up to eight possible permutations of values of costs of tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$) equal to either $0$ or $0.02$ [@Duthie observed $0.02$ to be a strong cost of tendency for polyandry] for values of $\beta = 3$ ($8$ total combinations). --->

<!--- In simulations without evolving $F_{p}$, we therefore include all $4$ combinations of $c_{P}=\{0,0.02\}$ and $c_{M}=\{0,0.02\}$ (but not $c{F}$). --->

@@

<!--- To test hypotheses regarding evolution under different relative costs of phenotypes, we consider all combinations of costs using simulations in which all three traits evolve. To test the hypothesis that pre-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($M_{p}<0$) when mating costs are low relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy, but that selection for post-copulatory inbreeding strategy will then be negligible ($F_{p} \approx 0$), we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where $c_{M}=0$ but $c_{P}$, $c_{F}$, or both equals $0.02$. We compare evolution in these three cost parameter value combinations with simulations in which all costs equal either $0$ or $0.02$. If our hypothesis is supported, then $M_{p}$ but not $F_{p}$ will evolve to more negative values when $c_{M}$ is relatively low than when all cost values are uniform. To test the hypothesis that post-copulatory inbreeding strategy will evolve toward inbreeding avoidance ($F_{p}<0$) given low costs of polyandry and post-copulatory inbreeding strategy relative to the cost of pre-copulatory inbreeding strategy, but that selection on pre-copulatory inbreeding strategy will be negligible ($M_{p} \approx 0$), we quantify evolution of $M_{p}$ and $F_{p}$ over generations when $c_{F}=0$, $c_{P}=0$, and $c_{M}=0.02$ . We compare evolution for this combination of cost parameter values with simulations in which all costs equal either $0$ or $0.02$. If our hypothesis is supported, then $F_{a}$ but not $M_{a}$ allele values will become more negative over generations when $c_{F}$ is relatively low than when all cost values are uniform. --->

<!--- To test the hypothesis that constraints on evolution of one inbreeding strategy will increase the strength of selection on a complementary strategy, we fixed inbreeding strategy phenotypes to values of zero, thereby causing either random mating ($M_{p}=0$) or the random fertilisation of offspring ($F_{p}=0$) according to a fair raffle among mates with respect to kinship. We then compare evolution of the non-fixed trait to its evolution in simulations where all traits are allowed to evolve. --->

@@

<!--- We present our results by showing mean allele value changes over generations. Figures 1-5 show mean allele values of tendency for polyandry ($P_{a}$; red lines and shading), pre-copulatory inbreeding strategy ($M_{a}$; blue lines and shading), and post-copulatory inbreeding strategy ($F_{a}$; black lines and shading) over 10000 generations as calculated across all individuals (female and male) within a focal population over 40 replicate simulations with identical starting conditions. Solid lines represent the grand mean of replicate mean allele values, and shading around lines shows standard errors of mean allele values around the grand mean. Panels within figures show different cost combinations for tendency for polyandry ($c_{P}$), pre-copulatory inbreeding strategy ($c_{M}$), and post-copulatory inbreeding strategy ($c_{F}$). Figures have fewer than eight panels if some costs are not relevant because allele values are fixed, and fixed allele values are shown as horizontal lines where line height is set to the fixed allele value. Supporting Information S1 presents correlations of mean allele values across replicate simulations, which were generally weak; we found no evidence suggesting strong evolutionary divergence among replicates with identical starting conditions (e.g., as might be the case if populations stochastically evolved toward inbreeding avoidance through mate choice or fertilisation, but not both), meaning that inspecting grand means of replicate allele values accurately reflects expected evolutionary dynamics over generations. --->

@@

<!--- We first test our hypothesis that a focal female's ability to express post-copulatory choice with respect to kinship causes selection for polyandry by comparing simulations in which post-copulatory inbreeding strategy is fixed to random mating with respect to kinship to simulations in which tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy can all evolve. --->

@@

<!--- Comparison of Figures 1 and 2 shows that evolution of post-copulatory inbreeding strategy facilitates evolution of polyandry, particularly when costs of tendency for polyandry and post-copulatory inbreeding strategy are zero. For example, in Figure 2A, tendency for polyandry allele values consistently become negative over generations ($P_{a}<0$; decreasing red line), causing populations to be monandrous. Females in these populations avoid mating with kin ($M_{a}<0$; decreasing blue line), and because these females sample mates with replacement, males that remain after their initial mate choice are more likely to be relatives, causing selection for monandry because females are most likely to succeed in avoiding inbreeding in their initial mate choice [see also @Duthie]. However, Figure 1A shows that when a focal female can also bias the probability that a particular mate sires her offspring, post-copulatory inbreeding strategy evolves to inbreeding avoidance ($F_{a}<0$; decreasing black line). Consequently, the ability to bias fertilisation to avoid inbreeding causes polyandry to become adaptive, and positive values of tendency for polyandry alleles increase in frequency ($P_{a}>0$; increasing red line of Figure 1A). Although non-zero costs decrease net selection for both tendency for polyandry and post-copulatory inbreeding strategy (see below), across all combinations of costs, tendency for polyandry allele values are more positive when post-copulatory inbreeding strategy can also evolve. Evolution of post-copulatory inbreeding avoidance therefore greatly facilitates evolution of polyandry. --->

@@

<!--- Some of these conclusions will need to be changed in light of the need for more generations of data: Strategies were concluded to be non-negligible, they they actually become negligible given a sufficient amount of time. --->

<!--- Our second hypothesis that selection for a costly inbreeding avoidance strategy will be negligible given a less costly alternative was generally supported by our simulations (Figure 3).  --->

@@

<!--- Figure 1 shows changes in mean allele values of tendency for polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy across all eight possible combinations of costs. In Figure 1A, when no phenotypes are costly, pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$). Costs of phenotypes had a direct effect on evolution, causing pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that were more negative (because realisation of polyandry costs increases with positive phenotype values). --->

<!--- We can use Figure 1 to test the hypothesis that pre-copulatory inbreeding strategy will evolve to inbreeding avoidance ($M_{a}<0$), but post-copulatory inbreeding strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and post-copulatory inbreeding strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A). Figure 1A,C,D,G show that inbreeding avoidance in mating ($M_{a}<0$) evolved consistently whenever $c_{M}=0$. When post-copulatory inbreeding strategy was costly and inbreeding avoidance strategy was not costly (Figure 1D,G), post-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($F_{a} < 0$), but long-term evolution of post-copulatory inbreeding strategy stabilised at random mating ($F_{a} \approx 0$). However, when only tendency for polyandry was costly (Figure 1C), both pre-copulatory inbreeding strategy and post-copulatory inbreeding strategy evolved to inbreeding avoidance over generations ($M_{a} < 0$ and $F_{a} < 0$). --->

<!--- We can also use Figure 1 to test the hypothesis that post-copulatory inbreeding strategy will evolve to inbreeding avoidance ($F_{a}<0$), but pre-copulatory inbreeding strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and post-copulatory inbreeding strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of pre-copulatory inbreeding strategy ($c_{M}=0.02$). Figure 1B shows that inbreeding avoidance through fertilisation bias evolved ($F_{a}<0$) under these conditions. While pre-copulatory inbreeding strategy initially evolved toward inbreeding avoidance ($M_{a} < 0$), long-term evolution of pre-copulatory inbreeding strategy stabilised at random mating ($M_{a} \approx 0$). --->

<!--- Selection given constraints on evolution --->
<!--- ---------------------------------------------- --->

<!--- Figure 3 shows evolution of tendency for polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$). For all cost combinations of tendency for polyandry and post-copulatory inbreeding strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of post-copulatory inbreeding strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias. This pattern of evolution contrasts with that observed when pre-copulatory inbreeding strategy was not fixed, indicating that constraints on evolution of pre-copulatory inbreeding strategy increased the strength of selection for evolution of polyandry and inbreeding avoidance through fertilisation bias. For example, in Figures 1C,D,G,H, tendency for polyandry allele values were typically less than zero, reflecting evolution of monandry, and post-copulatory inbreeding strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3). In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened. --->

<!--- Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of post-copulatory inbreeding strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle. In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry. However, values of pre-copulatory inbreeding strategy alleles did not greatly differ over generations when post-copulatory inbreeding strategy was fixed, meaning that the effect of fixed post-copulatory inbreeding strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible. A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean pre-copulatory inbreeding strategy allele value is $-0.627$ when post-copulatory inbreeding strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000. Because females have 20 alleles with additive effects on pre-copulatory inbreeding strategy, an average female was therefore expected to have mean pre-copulatory inbreeding strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed post-copulatory inbreeding strategy, respectively. These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed versus fixed post-copulatory inbreeding strategy, respectively. Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened. --->

@@

<!--- Our third hypothesis that invasion of pre- or post-copulatory inbreeding avoidance would be precluded by the existence of an already adaptive complementary strategy was supported for invading post-copulatory, but not pre-copulatory, inbreeding avoidance. --->

@@

<!--- Figure 4 shows change in pre-copulatory inbreeding strategy allele values over generations when tendency for polyandry and post-copulatory inbreeding strategy alleles were fixed for adaptive values of inbreeding avoidance $P_{a}=1$ and $F_{a}=-5$. Despite that females in these simulations could already avoid inbreeding after mating occurred, pre-copulatory inbreeding strategy evolved towards inbreeding avoidance given costs of $c_{M}=0$ (Figure 4A) and $c_{M}=0.02$ (Figure 4B). We therefore did not find evidence that the existence of adaptive inbreeding avoidance through fertilisation bias in any way precluded the evolution of adaptive inbreeding avoidance through mate choice. --->

<!--- Figure 5 shows change in tendency for polyandry and post-copulatory inbreeding strategy allele values over generations when pre-copulatory inbreeding strategy alleles were fixed for adaptive inbreeding avoidance $M_{a}=-5$. Existence of adaptive inbreeding avoidance through mate choice precluded evolution of polyandry for all combinations of costs (Figure 5), meaning that evolution of adpative polyandry to avoid inbreeding through post-copulatory inbreeding strategy was never predicted in populations where females were already avoiding inbreeding through mate choice. Further, while post-copulatory inbreeding strategy evolved toward inbreeding avoidance ($F_{a}<0$) in the absence of costs (Figure 5A,B), allele values of post-copulatory inbreeding strategy were not as negative as when adaptive inbreeding avoidance through mate choice was not fixed at the outset (Figures 1A,B,C,D). We therefore found strong evidence that the existence of adaptive inbreeding avoidance through pre-copulatory mate choice precluded evolution of adaptive inbreeding avoidance through post-copulatory inbreeding avoidance through fertilisation bias. --->

@@

<!--- ---------------------------------------------------------------------- --->
<!--- -------------------- LEFT OFF HERE ----------------------------------- --->
<!--- ---------------------------------------------------------------------- --->

<!--- Inbred offspring are typically less viable than outbred offspring, and when such inbreeding depression is strong, it is predicted to cause selection for inbreeding avoidance [Duthie and Reid *in press*; @Parker1979; @Parker2006; @Pusey1996; @Kokko2006]. In animals, inbreeding avoidance can be realised through both pre-copulatory and post-copulatory mechanisms [e.g., @Tuni2013; @Firman2015; @Daniel2015; @Fischer2015]. However, the conditions under which inbreeding avoidance is predicted to evolve via pre-copulatory, post-copulatory, or both pre- and post-copulatory mechanisms has not been modelled. There is therefore no framework for predicting what mechanisms of inbreeding avoidance are most likely to evolve in empirical populations where risk of fitness loss caused by inbreeding is high. Importantly, evolution of post-copulatory mechanisms of inbreeding avoidance requires females to mate multiply, meaning that post-copulatory inbreeding avoidance cannot occur unless polyandry has evolved in a population. Accordingly, --->

@@

<!--- Evolution of polyandry to avoid inbreeding --->
<!--- ---------------------------------------------- --->

@@

<!---Costs of polyandry and inbreeding avoidance --->
<!--- ---------------------------------------------- --->

<!---- Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1). Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$). Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased because each individual $P_{a}$ then became less influential in causing females to be monandrous [@Duthie]. This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998]. Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted to persist within populations even when costly [@Duthie], potentially creating the possibility for selection on post-copulatory inbreeding strategy when polyandry is expressed. This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line). Consequently, costly polyandry does not necessarily preclude evolution of adaptive post-copulatory inbreeding avoidance in populations. --->

@@

<!--- Constraints on polyandry and inbreeding avoidance --->
<!--- ---------------------------------------------- --->

@@

<!--- Constraints on pre-copulatory and post-copulatory inbreeding avoidance might vary widely in empirical systems. Female mate choice might be evolutionarily constrained if females are unable to discriminate among kin and therefore incapable of choosing to avoid inbreeding [Duthie and Reid *in press*; @Penn2010]. Similarly, females might choose to avoid inbreeding, but be ecologically constrained in their choice by the availability of males if few non-relatives are available [e.g., @Kokko2006a; @Kokko2013], or if females are unable to resist male coercion given sexual conflict [@Arnqvist2005, pp. 44-91]. Females might also be unable to discriminate between sperm of relatives versus non-relatives, or be unable to successfully bias fertilisation toward non-relative's sperm. Our results suggest that such constraints on one strategy of inbreeding avoidance (pre-copulatory versus post-copulatory) will strengthen selection on a complementary strategy, perhaps making inbreeding avoidance more detectable in empirical systems.  --->

<!--- Also: note, pre-copulatory but not post-copulatory inbreeding avoidance can occur for males --->

<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->

<!---  Constraints on pre-cop: Limited kin recognition --->

<!--- BARRIERS to having both pre and post-copulatory inbreeding avoidance evolve are few, although -- all else being equal -- post-copulatory avoidance might evolve less often if there is existing mating avoidance. --->

<!---  Concluding paragraph below --->

<!--- Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009]. Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*). These empirical studies demonstrate that evolution of all combinations of pre-copulatory and post-copulatory inbreeding avoidance are possible, but no general modelling attempts to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve. Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to be affected by direct costs, and constraints and adaptations of complementary inbreeding strategies. --->

<!---     ----------------------------------------------------------------     --->

>>>>

Inbreeding often reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012]. For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance). Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice is possible. As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms. Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007]. However, it remains unclear  <!--- Just fix this last sentence somehow... --->

@@

<!--- Probably want to clean up the below ---> 
In a recent model, @Duthie showed that selection for alleles underlying polyandry and pre-copulatory inbreeding avoidance occurred only under highly constrained conditions in which direct costs of polyandry were low, and when very few males were available during a female's initial mate choice but many males were available during a female's additional mate choice(s), or when polyandry was conditionally expressed based on the degree to which a focal female engaged in inbreeding given her initially chosen mate. In the absence of these constraints, expression of polyandry was expected to increase inbreeding with each additional mate because remaining males were more likely to be relatives once available non-relatives were chosen. However, @Duthie assumed that polyandrous females had no control over the assignment of paternity to their offspring. If after engaging in polyandry, females could bias paternity through post-copulatory mechanisms, then selection for polyandry to avoid inbreeding might be more widely predicted when inbreeding depression is severe [@Zeh1997].

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@
